### 2019-01-15 introduction.tex
finished data explanation and started traffic mix fixes

Keflavík International Airport (IATA: KEF, ICAO: BIKF) is the major gateway to Iceland currently with two functioning runways. The runways operate in both directions and are designated as RWY-01 (South-North), RWY-19 (North-South), RWY-10 (West-East) and RWY-28 (East-West). 
There has been an unforeseen increase of passengers travelling through Keflavík Airport in recent years, with over eight million passengers and 62.300 air transport movements in 2017~\cite{isavia_facts_2017}, where a movement is defined as an aircraft take-off or landing at an airport~\cite{aircraft_movement}. For 2018 the passenger numbers show a yearly growth of 13.44\% (at the time of writing) for the same time period from the previous year~\cite{isavia_pass_statistics_2018}. The increase in traffic at Keflavík Airport can and does experience constrained capacity of the runways during peak traffic periods. Airport capacity is generally defined as the number of movements per unit of time that can be accepted~\cite{airport_capacity_methodology}.

@@

The peak traffic hours are characterised by the time intervals when the airport operates at high loads. High load interval or window is at least 15 minutes in length and has four or more flights arriving or departing from Keflavík Airport. The time between flights during the high load interval is set at $\leq$4~minutes (Figure~\ref{fig:Peak_Diagram}). This value is based on statistical data by Isavia in order to achieve two distinct peak hours: one in the morning and one in the afternoon. The last flight in a high load window that fulfils these requirements is not considered to be a part of the peak as its behaviour is not affected by an instantaneous next flight after it.

>>>>

Keflavík International Airport (IATA: KEF, ICAO: BIKF) is the major gateway to Iceland and is serviced by Isavia~\cite{Isavia_about}. The airport currently has two functioning runways operating in both directions and are designated as RWY-01 (South-North), RWY-19 (North-South), RWY-10 (West-East) and RWY-28 (East-West). 
There has been an unforeseen increase of passengers travelling through Keflavík Airport in recent years, with over eight million passengers and 62.300 air transport movements in 2017~\cite{isavia_facts_2017}, where a movement is defined as an aircraft take-off or landing at an airport~\cite{aircraft_movement}. For 2018 the passenger numbers show a yearly growth of 13.44\% (at the time of writing) for the same time period from the previous year~\cite{isavia_pass_statistics_2018}. The increase in traffic at Keflavík Airport can and does experience constrained capacity of the runways during peak traffic periods. Airport capacity is generally defined as the number of movements per unit of time that can be accepted~\cite{airport_capacity_methodology}.

@@

The peak traffic hours are characterised by the time intervals when the airport operates at high loads. High load interval or window is at least 15 minutes in length and has five or more flights arriving or departing from Keflavík Airport. The time between flights during the high load interval is set at $\leq$4~minutes (Figure~\ref{fig:Peak_Diagram}). This value is based on statistical estimations by Isavia in order to achieve two distinct peak hours: one in the morning and one in the afternoon. The last flight in a high load window that fulfils these requirements is not considered to be a part of the peak as its behaviour is not affected by an instantaneous next flight after it.
